---
title: "Analysis 300-400 ms time window"
author: "Amélie la Roi"
date: "May 8, 2020"
output: html_document
---

Last update: September 2, 2020


# Data analysis on time window 300-400 ms

## Load packages
```{r warning=FALSE, results='hide'}
library(plyr)
library(dplyr)
library(lme4)
library(lmerTest)
library(emmeans)
library(multcomp)
library(effects)
library(ggplot2)
library(patchwork)
library(gridExtra)
library(grid)
library(pBrackets)
library(cowplot)


```


## Load data
```{r} 
# Load data study 3
print(load("G:/Back-up Y-schijf 12.03.2020/Study 3 - Follow-up MA thesis/Data/EEG/Preprocessing data/data_300-400_v3/S3.300-400_agg_v3.rdat"))

# Load data study 0
print(load("G:/Back-up Y-schijf 12.03.2020/Study 3 - Follow-up MA thesis/Data/EEG/Preprocessing data/data_300-400/300-400_agg.rdat"))

# Check variable names in dataframes
names(S3ALL.T2_agg)
names(all.T2_agg)

# Merge data study 0 and study 3
ALL2.T2 <- rbind(S3ALL.T2_agg, all.T2_agg) # 112880 + 338280 = 451160 observations --> correct!

# Check data
str(ALL2.T2) # Subject has 66 levels --> correct (50 (T1) + 16 (T2))

```

### Add session variable
```{r}
ALL2.T2$Session[ALL2.T2$Subject %in% c("1","5","9","10","12","15","16",
                                  "20","23","25","26","28","29","31",
                                  "34","36","40","41","46","47","49",
                                  "51","54","55","57","3","8","11","13",
                                  "14","17","18","21","22","24","27","33",
                                  "35","37","38","39","42","44","45","48",
                                  "50","52","53","56","58")] <- "T1"

ALL2.T2$Session[ALL2.T2$Subject %in% c("IAS30005_AR","IAS30009_AR","IAS30010_AR","IAS30016_AR","IAS30020_AR",
              "IAS30026_AR","IAS30029_AR","IAS30031_AR","IAS30034_AR","IAS30036_AR",
              "IAS30040_AR","IAS30041_AR","IAS30049_AR","IAS30051_AR",
              "IAS30054_AR","IAS30057_AR")] <- "T2"

ALL2.T2$Session <- as.factor(ALL2.T2$Session)

```


### Tidy variables
```{r results='hide'}
# Rename subject variable study 3
ALL2.T2$Subject <- revalue(ALL2.T2$Subject, c("IAS30005_AR"="5","IAS30009_AR"="9","IAS30010_AR"="10","IAS30016_AR"="16",
                         "IAS30020_AR"="20","IAS30026_AR"="26","IAS30029_AR"="29","IAS30031_AR"="31",
                         "IAS30034_AR"="34","IAS30036_AR"="36","IAS30040_AR"="40","IAS30041_AR"="41",
                         "IAS30049_AR"="49","IAS30051_AR"="51","IAS30054_AR"="54", "IAS30057_AR"="57"))

#check data
str(ALL2.T2) # Subject variable has 50 levels --> correct

# Only select data older adults
ALL3.T2 <- droplevels(ALL2.T2[ALL2.T2$Group == 'senior',])

# Check data
str(ALL3.T2) # Subject variable has 25 levels --> correct

# check dummy coding and relevel if necessary
contrasts(ALL3.T2$Session)

# check Context factor
ALL3.T2 <- rename(ALL3.T2, Context=Constraint) # rename factor to 'Context'
contrasts(ALL3.T2$Context)
ALL3.T2$Context <- relevel(ALL3.T2$Context, "Neutral")
ALL3.T2$Context <- revalue(ALL3.T2$Context, c("High"="Predictive")) # rename factor level 'High' to 'Predictive'
contrasts(ALL3.T2$Context)

# Check Idiomaticity factor
contrasts(ALL3.T2$Idiomaticity)
ALL3.T2$Idiomaticity <- relevel(ALL3.T2$Idiomaticity, "Lit")

# Check Correctness factor
ALL3.T2 <- rename(ALL3.T2, Correctness=Condition)
contrasts(ALL3.T2$Correctness)

# Check dataframe
head(ALL3.T2)
summary(ALL3.T2)
str(ALL3.T2)
```


# Create dataset for analysis
```{r results='hide'}
# Compute mean voltage over session, group, the 8 experimental conditions, and the 4 ROIs
ALL3.T2_agg <- ddply(ALL3.T2, c("Subject", "Session", "Group", "Context", "Idiomaticity", "Correctness", 
                                "TrialNr", "Target", "Anteriority", "Hemisphere", "ROI"), summarise, 
                                mean.mV = mean(mV, na.rm=TRUE),
                                subj.n = length(mV[!is.na(mV)]))

str(ALL3.T2_agg)
summary(ALL3.T2_agg)

# Only select posterior ROIs
ALL3.T2_post1 <- droplevels(ALL3.T2_agg[ALL3.T2_agg$Anteriority == 'post',])
str(ALL3.T2_post1)
summary(ALL3.T2_post1)

# Load VF data
print(load("G:/Back-up Y-schijf 12.03.2020/Study 3 - Follow-up MA thesis/Data/Cognitive tasks/Verbal fluency/S0S3_VF_final.rdat"))

# Remove redundant columns
VF_final <- subset(VF4, select=c(Subject, Session, Cat.c, Let.c, Total.c))

# Merge VF scores with EEG data
ALL3.T2_post <- merge(ALL3.T2_post1, VF_final, by=c("Subject", "Session"))
summary(ALL3.T2_post)

```


# Test for general longitudinal effects in the N400
```{r results='hide'}
# Average mean voltages over Context and Idiomaticity
ALL3.T2_N400 <- ddply(ALL3.T2_post, c("Subject", "Session", "Group", "Correctness", "TrialNr", "Target", "Anteriority", "Hemisphere", "ROI"), summarise, mean.mV = mean(mean.mV, na.rm=TRUE))

# Only select posterior ROIs
T2N400_post <- droplevels(ALL3.T2_N400[ALL3.T2_N400$Anteriority=='post',])

# Fit model on general N400 effect in baseline and follow-up session
m0.T2 <- lmer(mean.mV ~ Session * Correctness + Hemisphere + (1|Subject) + (1|Target), data=T2N400_post, control=lmerControl(optimizer="Nelder_Mead"), REML=F)
summary(m0.T2) # No interaction between Session * Correctness, so general N400 effect doesn't seem to change over time

# Compute contrasts
(T2_contrastN400_Correctness <- lsmeans(m0.T2, pairwise ~ Correctness|Session))
(T2_contrastN400_Session <- lsmeans(m0.T2, pairwise ~ Session|Correctness)) # incorrect significantly less negative at follow-up compared with baseline

# Change reference level of correctness to facilitate interpretation of planned comparisons on N400 effect
contrasts(T2N400_post$Correctness)
T2N400_post$Correctness <- relevel(T2N400_post$Correctness, "incorrect")

# Fit model again with relevel factor
m0a.T2 <- lmer(mean.mV ~ Session * Correctness + Hemisphere + (1|Subject) + (1|Target), data=T2N400_post, control=lmerControl(optimizer="Nelder_Mead"), REML=F)
summary(m0a.T2)

(T2_contrastN400_Correctness_v2 <- lsmeans(m0a.T2, pairwise ~ Correctness|Session))
(T2_contrastN400_Session_v2 <- lsmeans(m0a.T2, pairwise ~ Session|Correctness))

m0b.T2 <- lmer(mean.mV ~ Session + Correctness + Hemisphere + (1|Subject) + (1|Target), data=T2N400_post, control=lmerControl(optimizer="Nelder_Mead"), REML=F)
anova(m0a.T2, m0b.T2)
AIC(m0b.T2)-AIC(m0a.T2) # -0.91

summary(m0b.T2)

```

## Plot general longitudinal effects in the N400 effect

# Plot N400 effect in barplot
```{r}

# Compute mean voltage for correct and incorrect target words in baseline and follow-up session
plot_m0.T2 <- allEffects(m0.T2)
plot_m0.T2 # print effects

# Save interaction effect of the model in a dataframe
## 300-400 ms
T2intN400 <- plot_m0.T2[[2]] # save the interaction effect
T2intN400.df <- as.data.frame(T2intN400) # convert into dataframe

# Rename factor levels Session
levels(T2intN400.df$Session)[levels(T2intN400.df$Session)=="T1"] <- "Baseline"
levels(T2intN400.df$Session)[levels(T2intN400.df$Session)=="T2"] <- "Follow-up"
contrasts(T2intN400.df$Session)

# Make barplot
(TW2_N400_bar <- ggplot(data=T2intN400.df, aes(x=Session, y=fit, fill=Correctness)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black", size=1) +
  scale_fill_grey() + coord_cartesian(ylim=c(-1,4)) + scale_y_continuous(breaks=seq(-1,4,1)) +
  background_grid(major='none', minor="none") + labs(x=NULL, y="\nFitted values mV") +
  ggtitle("\n300-400 ms") + theme_classic() +
  theme(plot.title=element_text(size= 24, color="black", face="bold", hjust=0.5),
  axis.title.y=element_text(size=32, color="black", face="bold"), axis.text=element_text(size=28, color="black", face="bold"), axis.line=element_line(size=1), axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"), 
  legend.text=element_text(size=24, color="black"), legend.title=element_text(size=28, color="black", face="bold"),
  legend.position="bottom",
  plot.margin=margin(r=1, l=1, unit="cm"), panel.grid.major.y=element_blank())+
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.2, position=position_dodge(0.9)))


# Save plot
# ggsave(TW2_N400_bar, file="./Plots/Rplots/TW2_N400_bar.png", width=10, height=10, units="in")
# ggsave(TW2_N400_bar, file="./Plots/Rplots/TW2_N400_bar.pdf", width=10, height=10, units="in")
# ggsave(TW2_N400_bar, file="./Plots/Rplots/TW2_N400_bar.tiff", width=10, height=10, units="in")

```


## Prepare data for plotting N400 effects and P600 effects in lineplot
### Load the data  
```{r results='hide'}
# Load data study 3
print(load("./EEG - Final data/S3wholesegment_v3.rdat"))
str(S3ALL) # check whether variables contain correct number of levels --> yes

# Add session variable to study 3
S3ALL$Session <- "T2"
S3ALL$Session <- as.factor(S3ALL$Session)

# Revalue subject variable study 3
S3ALL$Subject <- revalue(S3ALL$Subject, c("IAS30005_AR"="5","IAS30009_AR"="9","IAS30010_AR"="10","IAS30016_AR"="16",
                         "IAS30020_AR"="20","IAS30026_AR"="26","IAS30029_AR"="29","IAS30031_AR"="31",
                         "IAS30034_AR"="34","IAS30036_AR"="36","IAS30040_AR"="40","IAS30041_AR"="41",
                         "IAS30049_AR"="49","IAS30051_AR"="51","IAS30054_AR"="54", "IAS30057_AR"="57"))

# Load data study 0
print(load("./EEG - Final data/wholesegment.rdat"))
str(ALL)
ALL$Constraint <- droplevels(ALL$Constraint)
ALL$Idiomaticity <- droplevels(ALL$Idiomaticity)
str(ALL)

# Add session variable to study 0
ALL$Session <- "T1"
ALL$Session <- as.factor(ALL$Session)

# Revalue subject variable study 0
ALL$Subject <- revalue(ALL$Subject, c("amtest_0001_Arf_final"="1","amtest_0005_Arf_final"="5",
                         "amtest_0009_Arf_final"="9","amtest_0010_Arf_final"="10",
                         "amtest_0012_Arf_final"="12","amtest_0015_Arf_final"="15",
                         "amtest_0016_Arf_final"="16","amtest_0020_Arf_final"="20",
                         "amtest_0023_Arf_final"="23","amtest_0025_Arf_final"="25",
                         "amtest_0026_Arf_final"="26","amtest_0028_Arf_final"="28",
                         "amtest_0029_Arf_final"="29","amtest_0031_Arf_final"="31",
                         "amtest_0034_Arf_final"="34","amtest_0036_Arf_final"="36",
                         "amtest_0040_Arf_final"="40","amtest_0041_Arf_final"="41",
                         "amtest_0046_Arf_final"="46","amtest_0047_Arf_final"="47",
                         "amtest_0049_Arf_final"="49","amtest_0051_Arf_final"="51",
                         "amtest_0054_Arf_final"="54","amtest_0055_Arf_final"="55",
                         "amtest_0057_Arf_final"="57","amtest_0003_Arf_final"="3",
                         "amtest_0008_Arf_final"="8",
                         "amtest_0011_Arf_final"="11","amtest_0013_Arf_final"="13",
                         "amtest_0014_Arf_final"="14","amtest_0017_Arf_final"="17",
                         "amtest_0018_Arf_final"="18","amtest_0021_Arf_final"="21",
                         "amtest_0022_Arf_final"="22","amtest_0024_Arf_final"="24",
                         "amtest_0027_Arf_final"="27","amtest_0033_Arf_final"="33",
                         "amtest_0035_Arf_final"="35","amtest_0037_Arf_final"="37",
                         "amtest_0038_Arf_final"="38","amtest_0039_Arf_final"="39",
                         "amtest_0042_Arf_final"="42","amtest_0044_Arf_final"="44",
                         "amtest_0045_Arf_final"="45","amtest_0048_Arf_final"="48",
                         "amtest_0050_Arf_final"="50","amtest_0052_Arf_final"="52",
                         "amtest_0053_Arf_final"="53","amtest_0056_Arf_final"="56",
                         "amtest_0058_Arf_final"="58"))

# Only select older adults study 0
ALL.senior <- droplevels(ALL[ALL$Group == 'senior',])
str(ALL.senior) # subject has now 25 levels --> correct

# Merge the two dataframes
names(S3ALL)
names(ALL.senior)

ALL2 <- rbind(ALL.senior, S3ALL) # 2286360 + 1610280 = 3896640 observations --> correct!
str(ALL2) # Subject has 25 levels --> correct

# Rename predictors
ALL2 <- rename(ALL2, Context=Constraint) # rename factor to 'Context'
ALL2 <- rename(ALL2, Correctness=TargetType) # rename factor to 'Correctness'
ALL2$Context <- revalue(ALL2$Context, c("High"="Predictive"))

# Check reference levels of factors
contrasts(ALL2$Context)
ALL2$Context <- relevel(ALL2$Context, "Neutral")

contrasts(ALL2$Idiomaticity)
ALL2$Idiomaticity <- relevel(ALL2$Idiomaticity, "Lit")

contrasts(ALL2$Correctness)
contrasts(ALL2$Session)
```


### Compute averages per session and group
```{r}
ALL2_agg <- ddply(ALL2, c("Session", "Group", "Timebin", "Anteriority", 
                          "Hemisphere", "Roi", "Context", "Idiomaticity", "Correctness"), summarise,
                          mean.mV = mean(mV, na.rm=TRUE),
                          subj.n = length(mV[!is.na(mV)]))

# check data
str(ALL2_agg)
range(ALL2_agg$mean.mV) # from -3.35 - +6.81
range(ALL2_agg$Timebin) # from -15 till +119

# create Time variable
ALL2_agg$Time <- ALL2_agg$Timebin*10
range(ALL2_agg$Time) # from -150 till 1190 --> correct
```


### Make dataframe for the two posterior ROIs

```{r}

# Posterior left
PostLeft <- droplevels(ALL2_agg[ALL2_agg$Roi == 'post.left',])
summary(PostLeft)

# Posterior right
PostRight <- droplevels(ALL2_agg[ALL2_agg$Roi == 'post.right',])
summary(PostRight)



## Average mean voltages over Context and Idiomaticity
PostLeft_N400 <- ddply(PostLeft, c("Group", "Time", "Hemisphere", "Session", "Correctness"), summarise,
                          mean.mV = mean(mean.mV, na.rm=TRUE))

PostRight_N400 <- ddply(PostRight, c("Group", "Time", "Hemisphere", "Session", "Correctness"), summarise,
                          mean.mV = mean(mean.mV, na.rm=TRUE))
  
```


# Plot N400 effects and P600 effects in line plots
```{r}
# Posterior left - Baseline
(PostLeftT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.35) +
  geom_line(data=PostLeft_N400[PostLeft_N400$Session =="T1",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Baseline\nPosterior left",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=24, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=24, face="bold", color="black"), 
                           axis.text=element_text(size=20, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"), 
                           legend.title=element_text(size=24, face="bold", color="black"),
                           legend.text=element_text(size=22, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Posterior right - Baseline
(PostRightT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.35) +
  geom_line(data=PostRight_N400[PostRight_N400$Session =="T1",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Baseline\nPosterior right",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=24, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=24, face="bold", color="black"), 
                           axis.text=element_text(size=20, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"), 
                           legend.title=element_text(size=24, face="bold", color="black"),
                           legend.text=element_text(size=22, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Posterior left - Follow-up
(PostLeftT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.35) +
  geom_line(data=PostLeft_N400[PostLeft_N400$Session =="T2",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Follow-up\nPosterior left",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=24, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=24, face="bold", color="black"), 
                           axis.text=element_text(size=20, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"), 
                           legend.title=element_text(size=24, face="bold", color="black"),
                           legend.text=element_text(size=22, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Posterior right - Follow-up
(PostRightT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.35) +
  geom_line(data=PostRight_N400[PostRight_N400$Session =="T2",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Follow-up\nPosterior right",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=24, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=24, face="bold", color="black"), 
                           axis.text=element_text(size=20, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"), 
                           legend.title=element_text(size=24, face="bold", color="black"),
                           legend.text=element_text(size=22, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Combine plots
## Delete legend
PostLeftT1_nolegend <- PostLeftT1 + theme(legend.position = "none")
PostRightT1_nolegend <- PostRightT1 + theme(legend.position = "none")
PostLeftT2_nolegend <- PostLeftT2 + theme(legend.position = "none")
PostRightT2_nolegend <- PostRightT2 + theme(legend.position = "none")

# Save legend
legendT1T2_line <- get_legend(PostLeftT1 + theme(legend.position = "bottom", legend.justification = "top"))

# Make one plot
(intN400P600_T1T2 <- grid.arrange(PostLeftT1_nolegend, PostRightT1_nolegend,
                                 PostLeftT2_nolegend, PostRightT2_nolegend,
                                        ncol=2, top=textGrob("General N400 effects & P600 effects",
                                        gp=gpar(fontsize=28, fontface="bold")), bottom=legendT1T2_line))

# Save plots
# ggsave(intN400P600_T1T2, file="./Plots/Rplots/intN400P600_T1T2.png", width=20, height=15, units="in")
# ggsave(intN400P600_T1T2, file="./Plots/Rplots/intN400P600_T1T2.pdf", width=20, height=15, units="in")
# ggsave(intN400P600_T1T2, file="./Plots/Rplots/intN400P600_T1T2.tiff", width=20, height=15, units="in")
```


# Model fitting
## Start with full model with by-Subject and by-Target(=item) random intercepts
```{r}
m1.T2 <- lmer(mean.mV ~ Session * Context * Idiomaticity * Correctness + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m1.T2) # significant interaction Session*Context*Idiomaticity; trend for Context*Correctness
```

## Remove Correctness from 4-way interaction
```{r}
m2.T2 <- lmer(mean.mV ~ Session * Idiomaticity * Context + Correctness + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m2.T2) # no significant interactions
AIC(m2.T2)-AIC(m1.T2) # no significant AIC difference (1.76)
anova(m2.T2, m1.T2) # 4-way interaction significantly improves model fit --> keep in 4-way interaction
```

## Remove Context from 4-way interaction
```{r}
m3.T2 <- lmer(mean.mV ~ Session * Idiomaticity * Correctness + Context + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m3.T2) # no significant interactions
AIC(m3.T2) - AIC(m1.T2) # model with 4-way interaction has lower AIC
anova(m3.T2, m1.T2) # 4-way interaction significantly improves model fit
```

## Remove Idiomaticity from 4-way interaction
```{r}
m4.T2 <- lmer(mean.mV ~ Session * Context * Correctness + Idiomaticity + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m4.T2)
AIC(m4.T2)-AIC(m1.T2) # model with 4-way interaction has lower AIC
anova(m4.T2, m1.T2) # 4-way interaction significantly improves model fit
```

## Remove Session from interaction
```{r}
m5.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m5.T2) # significant interaction Context * Idiomaticity * Correctness; main effect of Session
AIC(m5.T2) - AIC(m1.T2) # model with 3-way interaction has lower AIC
anova(m5.T2, m1.T2) # 4-way interaction doesn't significantly improve model fit

```

## Remove Context from 3-way interaction
```{r}
m6.T2 <- lmer(mean.mV ~ Session + Context + Idiomaticity * Correctness + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m6.T2) # no significant interaction
AIC(m6.T2) - AIC(m5.T2) # model with 3-way interaction has lower AIC
anova(m5.T2, m6.T2) # 3-way interaction significantly improves model fit

```

## Remove Idiomaticity from 3-way interaction
```{r}
m7.T2 <- lmer(mean.mV ~ Session + Idiomaticity + Context * Correctness + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m7.T2) # no significant interaction
AIC(m7.T2) - AIC(m5.T2) # model with 3-way interaction has lower AIC
anova(m5.T2, m7.T2) # 3-way interaction significantly improves model fit
```

## Remove Correctness from 3-way interaction
```{r}
m8.T2 <- lmer(mean.mV ~ Session + Correctness + Context * Idiomaticity + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m8.T2) # no significant interaction
AIC(m8.T2) - AIC(m5.T2) # model with 3-way interaction has lower AIC
anova(m5.T2, m8.T2) # 3-way interaction significantly improves model fit
```


### BEST MODEL SO FAR: m5.T2 

## Test effect of hemisphere
```{r}
# Test effect Hemisphere
m9.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=F)
summary(m9.T2) # Hemisphere is not significant
AIC(m9.T2)-AIC(m5.T2) # no AIC difference
anova(m9.T2, m5.T2) # including Hemisphere does not improve model fit, but leave in for clarity
```

## Add random slopes
```{r}
# Add random slope for Idiomaticity per Subject
m10.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + (1+Idiomaticity|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=T)
summary(m10.T2)

# Fit model with REML=T to compare to random slope model
m9a.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + (1|Subject) + (1|Target), data=ALL3.T2_post, control=lmerControl(optimizer="bobyqa"), REML=T)

anova(m9a.T2, m10.T2) # model with random slope is significantly better

# Add random slope for Context per Target
m11.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + (1+Idiomaticity|Subject) + (1+Context|Target), data=ALL3.T2_post, control=lmerControl(optimizer="Nelder_Mead"), REML=T)
summary(m11.T2)

anova(m10.T2, m11.T2) # model with both random slopes is significantly better

```


## Test effect Verbal fluency
```{r}

# Fit m8.T2 with REML=F to enable model comparison
m11a.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + (1+Idiomaticity|Subject) + (1+Context|Target), data=ALL3.T2_post, control=lmerControl(optimizer="nlminbwrap"), REML=F)

# Test effect category fluency
m12.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + Cat.c + (1+Idiomaticity|Subject) + (1+Context|Target), data=ALL3.T2_post, control=lmerControl(optimizer="nlminbwrap"), REML=F)
summary(m12.T2)# Category fluency is not significant
AIC(m12.T2)-AIC(m11a.T2) # no difference in AIC
anova(m12.T2, m11a.T2) # inclusion of category fluency doesn't sigificantly improve model fit

# Test effect letter fluency
m13.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + Let.c + (1+Idiomaticity|Subject) + (1+Context|Target), data=ALL3.T2_post, control=lmerControl(optimizer="nlminbwrap"), REML=F)
summary(m13.T2)# Letter fluency is not significant
AIC(m11a.T2)-AIC(m13.T2) # no difference in AIC
anova(m11a.T2, m13.T2) # inclusion of letter fluency doesn't sigificantly improve model fit

```



# BEST MODEL SO FAR: m11.T2 


## Check distribution of residuals and trim model if needed
## Use model with interaction to check if interaction comes out after outliers have been removed
```{r}
qqnorm(resid(m11.T2))
qqline(resid(m11.T2)) # skewed distribution, some extreme outliers
plot(fitted(m11.T2), resid(m11.T2)) # some extreme outliers
hist(resid(m11.T2)) # looks pretty normal, except for few extreme outliers

## trim data
ALL3.T2_post.trim <- ALL3.T2_post[abs(scale(resid(m11.T2))) < 2.5, ]

## save trimmed data
save(ALL3.T2_post.trim, file="./EEG - Final data/ALL3.T2_post.trim.rdat" )

## fit model with trimmed data
m11b.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + (1+Idiomaticity|Subject) + (1+Context|Target), data=ALL3.T2_post.trim, control=lmerControl(optimizer="nlminbwrap"), REML=T)
summary(m11b.T2) # 3-way interaction is still significant

## check how much data was removed
(noutliers <- sum(abs(scale(resid(m11.T2))) >= 2.5))
noutliers/nrow(ALL3.T2_post) # only 1.8 % of the data was removed

## check change in correlation between observed and fitted values after trimming the data
cor(ALL3.T2_post$mean.mV, fitted(m11.T2))^2 # is 0.148
cor(ALL3.T2_post.trim$mean.mV, fitted(m11b.T2))^2 # increased to 0.164

## check distribution of residuals after trimming
qqnorm(resid(m11b.T2))
qqline(resid(m11b.T2)) # better distribution
plot(fitted(m11b.T2), resid(m11b.T2)) # better
hist(resid(m11b.T2)) # looks normal
```

# Final model: m11b.T2 (for summmary of coefficients final model set REML to TRUE)

## To get insight in the direction of the interactions between Context x Idiomaticity x Correctness, calculate contrasts
```{r}
# 3-way interaction
(T2_contrast_Correctness <- lsmeans(m11b.T2, pairwise ~ Correctness|Context|Idiomaticity)) # incorrect more negative than correct in all conditions

(T2_contrast_Idiom <- lsmeans(m11b.T2, pairwise ~ Idiomaticity|Correctness|Context)) # Idiom significantly more positive than Lit in Neutral correct and in Predictive incorrect

(T2_contrast_Context <- lsmeans(m11b.T2, pairwise ~ Context|Idiomaticity|Correctness)) # Predictive significantly more positive than Neutral only in Lit correct


# visualize interaction
lsmip(m11b.T2, Correctness ~ Idiomaticity|Context) 

lsmip(m11b.T2, Idiomaticity ~ Correctness|Context) # shows effect of Idiomaticity

lsmip(m11b.T2, Context ~ Correctness|Idiomaticity) # shows context effect in Lit correct
```

## Change reference of Correctness to make contrast more interpretable
```{r}
ALL3.T2_post.trim$Correctness <- relevel(ALL3.T2_post.trim$Correctness, "incorrect")

# Fit model again with releveled factor
m11c.T2 <- lmer(mean.mV ~ Session + Context * Idiomaticity * Correctness + Hemisphere + (1+Idiomaticity|Subject) + (1+Context|Target), data=ALL3.T2_post.trim, control=lmerControl(optimizer="nlminbwrap"), REML=T)

# Compute contrast again
(T2_contrast_Correctness <- lsmeans(m11c.T2, pairwise ~ Correctness|Context|Idiomaticity))

# Set reference level Correctness back to "correct"
ALL3.T2_post.trim$Correctness <- relevel(ALL3.T2_post.trim$Correctness, "correct")
```

### Save final model
```{r}

save(m11b.T2, file="./EEG - Final data/m11b.T2.rdat")

```


## Present interaction Context x Idiomaticity x Correctness in barplot
```{r, fig.height=5, fig.width=10}
# Save effects for the model

## 300-400 ms
plot_m11b.T2 <- allEffects(m11b.T2)
plot_m11b.T2 # print effects

# Save interaction effect of the model in a dataframe
## 300-400 ms
T2int <- plot_m11b.T2[[3]] # save the interaction effect
T2int.df <- as.data.frame(T2int) # convert into dataframe


# Check reference levels
# Factor Context
contrasts(T2int.df$Context) # Neutral is reference level --> correct

# Factor Idiomaticity
contrasts(T2int.df$Idiomaticity) # Idiom is reference level --> relevel
T2int.df$Idiomaticity <- factor(T2int.df$Idiomaticity, levels=c("Lit", "Idiom"))
contrasts(T2int.df$Idiomaticity) # Now Lit is reference level --> correct

# Rename factor levels Idiomaticity
levels(T2int.df$Idiomaticity)[levels(T2int.df$Idiomaticity)=="Lit"] <- "Literal"
levels(T2int.df$Idiomaticity)[levels(T2int.df$Idiomaticity)=="Idiom"] <- "Idiomatic"
contrasts(T2int.df$Idiomaticity)

# Factor Correctness
contrasts(T2int.df$Correctness) # correct is reference level

# Print range mV
range(T2int.df$fit) # 0.92 till 2.63


## Plot interaction Context * Idiomaticity * Correctness
### Literal sentences
(TW2_Lit_bar <- ggplot(data=T2int.df[T2int.df$Idiomaticity=="Literal",], aes(x=Context, y=fit, fill=Correctness)) +
  geom_bar(stat="identity", position=position_dodge(), linetype=0) +
  scale_fill_grey() + coord_cartesian(ylim=c(-1,4)) + scale_y_continuous(breaks=seq(-1,4,1)) +
  background_grid(major='y', minor="none") + labs(x=NULL, y="\nFitted values mV") +
  ggtitle("300-400 ms\nLiteral sentences") + theme_classic() +
  theme(plot.title=element_text(size= 16, color="black", face="bold", hjust=0.5), axis.title.y=element_text(size=16, color="black", face="bold"), axis.text=element_text(size=16, color="black", face="bold"), legend.text=element_text(size=14, color="black"),
legend.title=element_text(size=16, color="black", face="bold"), plot.margin=margin(r=1, l=1, unit="cm"), panel.grid.major.y=element_line(colour="lightgrey", size=0.2))+
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.2, position=position_dodge(0.9)))

### Predictive context
(TW2_Idiom_bar <- ggplot(data=T2int.df[T2int.df$Idiomaticity=="Idiomatic",], aes(x=Context, y=fit, fill=Correctness)) +
  geom_bar(stat="identity", position=position_dodge(), linetype=0) +
  scale_fill_grey() + coord_cartesian(ylim=c(-1,4)) + scale_y_continuous(breaks=seq(-1,4,1)) +
  background_grid(major='y', minor="none") + labs(x=NULL, y="\nFitted values mV") +
  ggtitle("300-400 ms\nIdiomatic sentences") + theme_classic() +
  theme(plot.title=element_text(size= 16, color="black", face="bold", hjust=0.5), axis.title.y=element_text(size=16, color="black", face="bold"), axis.text=element_text(size=16, color="black", face="bold"), legend.text=element_text(size=14, color="black"),
legend.title=element_text(size=16, color="black", face="bold"), plot.margin=margin(r=1, l=1, unit="cm"), panel.grid.major.y=element_line(colour="lightgrey", size=0.2))+
  geom_errorbar(aes(ymin=fit-se, ymax=fit+se), width=0.2, position=position_dodge(0.9)))

# Combine plots
## Delete legend
TW2_Lit_bar_nolegend <- TW2_Lit_bar + theme(legend.position = "none")
TW2_Idiom_bar_nolegend <- TW2_Idiom_bar + theme(legend.position = "none")

# Save legend
legendN400TW2 <- get_legend(TW2_Lit_bar + theme(legend.position = "bottom", legend.justification = "top"))

# Make one plot
(intN400_TW2 <- grid.arrange(TW2_Lit_bar_nolegend, TW2_Idiom_bar_nolegend,
                                        ncol=2, top=textGrob("300-400 ms\n",
                                        gp=gpar(fontsize=16, fontface="bold")), bottom=legendN400TW2))

# Add significance stars
## Write function to add brackets and save plot
bracketsGrob <- function(...){
l <- list(...)
e <- new.env()
e$l <- l
  grid:::recordGrob(  {
    do.call(grid.brackets, l)
  }, e)
}

# Define position of brackets
## Literal sentences
b1 <- bracketsGrob(0.18, 0.85, 0.37, 0.85, h=0.02, lwd=1, col="black", type=1, ticks=NULL) # Literal incorrect - correct
b2 <- bracketsGrob(0.63, 0.85, 0.82, 0.85, h=0.02,  lwd=1, col="black", type=1, ticks=NULL) # Idiomatic incorrect - correct
b3 <- bracketsGrob(0.63, 0.15, 0.18, 0.15, h=0.02,  lwd=1, col="black", type=1, ticks=NULL) # correct literal - idiomatic


## Add brackets and significance stars to plot
(intN400_TW2_Lit <- TW2_Lit_bar + 
                    annotation_custom(b1) + annotation_custom(b2) + 
                    annotation_custom(b3) + 
                    annotate("text", label="**", x=1.00, y= 3.60) + # Neut Lit incorrect - correct
                    annotate("text", label="***", x=2.00, y= 3.60) + # Pred Lit incorrect - correct
                    annotate("text", label="**", x=1.30, y= -0.65))  # Lit Correct Pred-Neut

## Idiomatic sentences
b1 <- bracketsGrob(0.18, 0.85, 0.37, 0.85, h=0.02, lwd=1, col="black", type=1, ticks=NULL) # Literal incorrect - correct
b2 <- bracketsGrob(0.63, 0.85, 0.82, 0.85, h=0.02,  lwd=1, col="black", type=1, ticks=NULL) # Idiomatic incorrect - correct
b3 <- bracketsGrob(0.63, 0.15, 0.18, 0.15, h=0.02,  lwd=1, col="black", type=1, ticks=NULL) # correct literal - idiomatic


## Add brackets and significance stars to plot
(intN400_TW2_Idiom <- TW2_Idiom_bar + 
                    annotation_custom(b1) + annotation_custom(b2) + 
                    annotate("text", label="***", x=1.00, y= 3.60) + # Neut Idiom incorrect - correct
                    annotate("text", label="***", x=2.00, y= 3.60)) + # Pred Idiom incorrect - correct

## Combine plots literal and idiomatic sentences
(TW2_ContIdiomCor_bar <- cowplot::plot_grid(intN400_TW2_Lit + theme(legend.position="bottom"),
                            intN400_TW2_Idiom + theme(legend.position="bottom"),
                            ncol=2, nrow=1, align='vh'))
  
# Save plot
# ggsave(TW2_ContIdiomCor_bar, file="./Plots/Rplots/TW2_ContIdiomCor_bar.png", width=10, height=5, units="in")
# ggsave(TW2_ContIdiomCor_bar, file="./Plots/Rplots/TW2_ContIdiomCor_bar.pdf", width=10, height=5, units="in")
# ggsave(TW2_ContIdiomCor_bar, file="./Plots/Rplots/TW2_ContIdiomCor_bar.tiff", width=10, height=5, units="in")
```


## Present interaction Context x Idiomaticity x Correctness in lineplot
### Separately for baseline and follow-up session
#### Baseline - Literal sentences
```{r, fig.width=20, fig.height=15}

# Baseline - Posterior left - Neutral context - Literal sentences
(NeutLitPostLeftT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostLeft[PostLeft$Session =="T1" & PostLeft$Idiomaticity=="Lit" & PostLeft$Context == "Neutral",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior left\nNeutral - Literal", y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Baseline - Posterior right - Neutral context - Literal sentences
(NeutLitPostRightT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostRight[PostRight$Session =="T1" & PostRight$Idiomaticity=="Lit" & PostRight$Context == "Neutral",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior right\nNeutral - Literal", y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Baseline - Posterior left - Predictive context - Literal sentences
(PredLitPostLeftT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostLeft[PostLeft$Session =="T1" & PostLeft$Idiomaticity=="Lit" & PostLeft$Context == "Predictive",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior left\nPredictive - Literal", y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Baseline - Posterior right - Predictive context - Literal sentences
(PredLitPostRightT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostRight[PostRight$Session =="T1" & PostRight$Idiomaticity=="Lit" & PostRight$Context == "Predictive",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior right\nPredictive - Literal", y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))



# Combine plots
## Delete legend
NeutLitPostLeftT1_nolegend <- NeutLitPostLeftT1 + theme(legend.position = "none")
NeutLitPostRightT1_nolegend <- NeutLitPostRightT1 + theme(legend.position = "none")
PredLitPostLeftT1_nolegend <- PredLitPostLeftT1 + theme(legend.position = "none")
PredLitPostRightT1_nolegend <- PredLitPostRightT1 + theme(legend.position = "none")


# Save legend
legendN400T1_line <- get_legend(NeutLitPostLeftT1 + theme(legend.position = "bottom", legend.justification = "top"))

# Make one plot
(intN400_T1_Lit <- grid.arrange(NeutLitPostLeftT1_nolegend, NeutLitPostRightT1_nolegend,
                                 PredLitPostLeftT1_nolegend, PredLitPostRightT1_nolegend,
                                        ncol=2, top=textGrob("Baseline session\nLiteral sentences",
                                        gp=gpar(fontsize=32, fontface="bold")), bottom=legendN400T1_line))

# Save plots
# ggsave(intN400_T1_Lit, file="./Plots/Rplots/intN400_T1_Lit.png", width=20, height=15, units="in")
# ggsave(intN400_T1_Lit, file="./Plots/Rplots/intN400_T1_Lit.pdf", width=20, height=15, units="in")
# ggsave(intN400_T1_Lit, file="./Plots/Rplots/intN400_T1_Lit.tiff", width=20, height=15, units="in")
```


### Baseline - Idiomatic sentences
```{r, fig.width=20, fig.height=15}

# Baseline - Posterior left - Neutral context - Idiomatic sentences
(NeutIdiomPostLeftT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostLeft[PostLeft$Session =="T1" & PostLeft$Idiomaticity=="Idiom" & PostLeft$Context == "Neutral",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior left\nNeutral - Idiomatic",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Baseline - Posterior right - Neutral context - Idiomatic sentences
(NeutIdiomPostRightT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostRight[PostRight$Session =="T1" & PostRight$Idiomaticity=="Idiom" & PostRight$Context == "Neutral",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior right\nNeutral - Idiomatic",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Baseline - Posterior left - Predictive context - Idiomatic sentences
(PredIdiomPostLeftT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostLeft[PostLeft$Session =="T1" & PostLeft$Idiomaticity=="Idiom" & PostLeft$Context == "Predictive",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior left\nPredictive - Idiomatic",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Baseline - Posterior right - Predictive context - Idiomatic sentences
(PredIdiomPostRightT1 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostRight[PostRight$Session =="T1" & PostRight$Idiomaticity=="Idiom" & PostRight$Context == "Predictive",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior right\nPredictive - Idiomatic",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))



# Combine plots
## Delete legend
NeutIdiomPostLeftT1_nolegend <- NeutIdiomPostLeftT1 + theme(legend.position = "none")
NeutIdiomPostRightT1_nolegend <- NeutIdiomPostRightT1 + theme(legend.position = "none")
PredIdiomPostLeftT1_nolegend <- PredIdiomPostLeftT1 + theme(legend.position = "none")
PredIdiomPostRightT1_nolegend <- PredIdiomPostRightT1 + theme(legend.position = "none")


# Save legend
legendN400T1_line <- get_legend(NeutIdiomPostLeftT1 + theme(legend.position = "bottom", legend.justification = "top"))

# Make one plot
(intN400_T1_Idiom <- grid.arrange(NeutIdiomPostLeftT1_nolegend, NeutIdiomPostRightT1_nolegend,
                                 PredIdiomPostLeftT1_nolegend, PredIdiomPostRightT1_nolegend,
                                        ncol=2, top=textGrob("Baseline session\nIdiomatic sentences",
                                        gp=gpar(fontsize=32, fontface="bold")), bottom=legendN400T1_line))

# Save plots
# ggsave(intN400_T1_Idiom, file="./Plots/Rplots/intN400_T1_Idiom.png", width=20, height=15, units="in")
# ggsave(intN400_T1_Idiom, file="./Plots/Rplots/intN400_T1_Idiom.pdf", width=20, height=15, units="in")
# ggsave(intN400_T1_Idiom, file="./Plots/Rplots/intN400_T1_Idiom.tiff", width=20, height=15, units="in")
```

#### Follow-up - Literal sentences
```{r, fig.width=20, fig.height=15}

# Follow-up - Posterior left - Neutral context - Literal sentences
(NeutLitPostLeftT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostLeft[PostLeft$Session =="T2" & PostLeft$Idiomaticity=="Lit" & PostLeft$Context == "Neutral",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior left\nNeutral - Literal",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Follow-up - Posterior right - Neutral context - Literal sentences
(NeutLitPostRightT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostRight[PostRight$Session =="T2" & PostRight$Idiomaticity=="Lit" & PostRight$Context == "Neutral",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior right\nNeutral - Literal",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Follow-up - Posterior left - Predictive context - Literal sentences
(PredLitPostLeftT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostLeft[PostLeft$Session =="T2" & PostLeft$Idiomaticity=="Lit" & PostLeft$Context == "Predictive",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior left\nPredictive - Literal",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Follow-up - Posterior right - Predictive context - Literal sentences
(PredLitPostRightT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostRight[PostRight$Session =="T2" & PostRight$Idiomaticity=="Lit" & PostRight$Context == "Predictive",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior right\nPredictive - Literal",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))



# Combine plots
## Delete legend
NeutLitPostLeftT2_nolegend <- NeutLitPostLeftT2 + theme(legend.position = "none")
NeutLitPostRightT2_nolegend <- NeutLitPostRightT2 + theme(legend.position = "none")
PredLitPostLeftT2_nolegend <- PredLitPostLeftT2 + theme(legend.position = "none")
PredLitPostRightT2_nolegend <- PredLitPostRightT2 + theme(legend.position = "none")


# Save legend
legendN400T2_line <- get_legend(NeutLitPostLeftT2 + theme(legend.position = "bottom", legend.justification = "top"))

# Make one plot
(intN400_T2_Lit <- grid.arrange(NeutLitPostLeftT2_nolegend, NeutLitPostRightT2_nolegend,
                                 PredLitPostLeftT2_nolegend, PredLitPostRightT2_nolegend,
                                        ncol=2, top=textGrob("Follow-up session\nLiteral sentences",
                                        gp=gpar(fontsize=32, fontface="bold")), bottom=legendN400T2_line))

# Save plots
# ggsave(intN400_T2_Lit, file="./Plots/Rplots/intN400_T2_Lit.png", width=20, height=15, units="in")
# ggsave(intN400_T2_Lit, file="./Plots/Rplots/intN400_T2_Lit.pdf", width=20, height=15, units="in")
# ggsave(intN400_T2_Lit, file="./Plots/Rplots/intN400_T2_Lit.tiff", width=20, height=15, units="in")
```


#### Follow-up - Idiomatic sentences
```{r, fig.width=20, fig.height=15}

# Follow-up - Posterior left - Neutral context - Idiomatic sentences
(NeutIdiomPostLeftT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostLeft[PostLeft$Session =="T2" & PostLeft$Idiomaticity=="Idiom" & PostLeft$Context == "Neutral",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior left\nNeutral - Idiomatic",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=24, face="bold", color="black"),
                           legend.text=element_text(size=24, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Follow-up - Posterior right - Neutral context - Idiomatic sentences
(NeutIdiomPostRightT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostRight[PostRight$Session =="T2" & PostRight$Idiomaticity=="Idiom" & PostRight$Context == "Neutral",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior right\nNeutral - Idiomatic",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Follow-up - Posterior left - Predictive context - Idiomatic sentences
(PredIdiomPostLeftT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostLeft[PostLeft$Session =="T2" & PostLeft$Idiomaticity=="Idiom" & PostLeft$Context == "Predictive",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior left\nPredictive - Idiomatic",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=24, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))

# Follow-up - Posterior right - Predictive context - Idiomatic sentences
(PredIdiomPostRightT2 <- ggplot() + geom_rect(data = data.frame(xmin = 300, xmax = 400, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 400, xmax = 500, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="green", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
   geom_rect(data = data.frame(xmin = 500, xmax = 800, ymin = -2.5, ymax = 7),
            aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), fill="red", colour="black", size=0.75, linetype="dotted", alpha = 0.5) +
  geom_line(data=PostRight[PostRight$Session =="T2" & PostRight$Idiomaticity=="Idiom" & PostRight$Context == "Predictive",], 
                           aes(x=Time, y=mean.mV, colour=Correctness, linetype=Correctness, size=Correctness)) + 
                           scale_color_manual(values=c("black", "black")) +
                           scale_linetype_manual(values=c("solid","dashed")) +
                           scale_size_manual(values=c(1,1)) +
                           scale_x_continuous(limits=c(-150, 1200), breaks=c(-150,0,200,400,600,800,1000,1200)) +
                           scale_y_reverse(lim=c(7,-2.5), breaks=c(6,4,2,0,-2)) +
                           labs(title="Posterior right\nPredictive - Idiomatic",
                           y="mV", x="\nTime\n") +
                           geom_hline(yintercept=0, linetype="dotted", size=0.5) +
                           geom_vline(xintercept=0, linetype="dotted",size=0.5) +
                           theme_classic() +
                           theme(plot.title=element_text(size=28, face="bold", color="black", hjust=0.5), 
                           axis.title=element_text(size=28, face="bold", color="black"), 
                           axis.text=element_text(size=24, face="bold", color="black"),
                           axis.text.x=element_text(vjust=-2),
                           axis.ticks = element_line(size=1), axis.ticks.length = unit(0.3,"cm"),
                           legend.title=element_text(size=28, face="bold", color="black"),
                           legend.text=element_text(size=26, face="bold", color="black"),
                           plot.margin=margin(r=1,l=0.5, unit="cm"),
                           legend.key=element_blank(),
                           legend.key.width=unit(2, "cm"),
                           legend.position="bottom", 
                           legend.box.background=element_blank()))



# Combine plots
## Delete legend
NeutIdiomPostLeftT2_nolegend <- NeutIdiomPostLeftT2 + theme(legend.position = "none")
NeutIdiomPostRightT2_nolegend <- NeutIdiomPostRightT2 + theme(legend.position = "none")
PredIdiomPostLeftT2_nolegend <- PredIdiomPostLeftT2 + theme(legend.position = "none")
PredIdiomPostRightT2_nolegend <- PredIdiomPostRightT2 + theme(legend.position = "none")


# Save legend
legendN400T2_line <- get_legend(NeutIdiomPostLeftT2 + theme(legend.position = "bottom", legend.justification = "top"))

# Make one plot
(intN400_T2_Idiom <- grid.arrange(NeutIdiomPostLeftT2_nolegend, NeutIdiomPostRightT2_nolegend,
                                 PredIdiomPostLeftT2_nolegend, PredIdiomPostRightT2_nolegend,
                                        ncol=2, top=textGrob("Follow-up session\nIdiomatic sentences",
                                        gp=gpar(fontsize=32, fontface="bold")), bottom=legendN400T2_line))

# Save plots
# ggsave(intN400_T2_Idiom, file="./Plots/Rplots/intN400_T2_Idiom.png", width=20, height=15, units="in")
# ggsave(intN400_T2_Idiom, file="./Plots/Rplots/intN400_T2_Idiom.pdf", width=20, height=15, units="in")
# ggsave(intN400_T2_Idiom, file="./Plots/Rplots/intN400_T2_Idiom.tiff", width=20, height=15, units="in")
```

